Types from data: \textnormal{Making structured data first-class citizens in F\#}

### 2016-02-09 pldi-2016/paper.tex
Typos

We include two numerical primitives, \ident{int} for integers and \ident{float} for floating-point 
numbers. The two are related by the perference relation and we prefer \ident{int}.

@@

We now specify how we obtain the shape from data. As clrified later (\S\ref{sec:impl-parsing}), 
we represent JSON, XML and CSV documents using the same first-order \emph{data} value:

@@

Primitive  values are mapped to their corresponding shapes. 
When infering a shape from multiple samples, we use the common preferred shape relation to find a 
common shape for all values (starting with $\bot$). This operation is used  
when calling a type provider with multiple samples and also when inferring the shape of collection
elements.

@@

\item Class members are renamed to follow \ident{PascalCase} naming convention, when a 
  colision occurs, a number is appended to the end as in \ident{PascalCase2}. The provided
  implementation preforms the lookup using the original name.
\end{itemize}

>>>>

We include two numerical primitives, \ident{int} for integers and \ident{float} for floating-point 
numbers. The two are related by the preference relation and we prefer \ident{int}.

@@

We now specify how we obtain the shape from data. As clarified later (\S\ref{sec:impl-parsing}), 
we represent JSON, XML and CSV documents using the same first-order \emph{data} value:

@@

Primitive  values are mapped to their corresponding shapes. 
When inferring a shape from multiple samples, we use the common preferred shape relation to find a 
common shape for all values (starting with $\bot$). This operation is used  
when calling a type provider with multiple samples and also when inferring the shape of collection
elements.

@@

\item Class members are renamed to follow \ident{PascalCase} naming convention, when a 
  collision occurs, a number is appended to the end as in \ident{PascalCase2}. The provided
  implementation preforms the lookup using the original name.
\end{itemize}
